\sys: Controllable Program Regeneration\\{\vspace{1em}\normalsize DTU MSc Thesis \\ Advisors: Christian Gram Kahlauge and Nikos Vasilakis

### 2025-07-17 docs/paper/draft.tex
Fix title and add LoC
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>

\documentclass[noacm,sigplan,review]{acmart}

@@

\title{\sys: Controllable Program Regeneration}
\author{Evangelos Lamprou}

@@

% add figure
\begin{figure}[htpb]
\centering
  % https://docs.google.com/drawings/d/1JdOfgpaVUy7_EgFyguRXHxFKdmZwyHaiHshnifHG0TQ/edit?usp=sharing
  \includegraphics[width=.9\columnwidth]{figs/kvasir_logic-space.pdf}
  \caption{\textbf{\sys transforms a program over its properties from the abstract logic space to the concrete space.}
  Relationships between properties of the original and regenerated program are inferred 
  from the query in combination with the knowledge base and enforced by \sys plugins.
  }
  \label{fig:logic-to-concrete}
\end{figure}

@@

\begin{table*}[htpb]
\centering
  \caption{\textbf{Benchmark summary}. 
  Benchmark programs come from online repositories, public archives, security research datasets, and often referenced examples in programming culture.
The N column shows the number of programs/functions from each benchmark.
}
  \begin{tabular*}{\textwidth}{llrrll}
\toprule
Benchmark                          & Description        & N  & LoC  & Task                   & Source \\
\midrule
Rosetta Code                       & Simple tasks       & 16 &      & Translation            & \cite{rosettacode} \\
Short utilities                    & npm/PyPi utilities & 13 &      & Parity                 & \cite{regbench2025} \\
SSCA                               & Sneaky supply-chain attacks        & 3  &      & Attack elimination     & \cite{ev:eurosec:2022, ohm2020backstabber,copeland2019frightening} \\
IOCCC                              & Obfuscated C code       & 2  &      & De-obfuscation         & \cite{ioccc} \\
Microbenchmarks                    &                    & 3  &      &                        & \\
\hspace{.5em} \ttt{flatmap-stream} & Flat-map utility   &    &      & Purity and translation & \cite{es1}  \\
\hspace{.5em} \ttt{Q\_rsqrt}       & Inverse square root function       &    &      & Idiomatic rewrite      & \cite{fast_inv_sqrt}  \\
\hspace{.5em} \textsf{rigidDB}     & Fetch artist songs from a music database     &    &      & Modularization         & \cite{codewithsadeemusicplayer} \\
\midrule
Total                              &                    & 37 &      &                        & \\
\bottomrule
\end{tabular*}
\label{tab:benchmarks}
\end{table*}

>>>>

\documentclass[nonacm,sigplan,review]{acmart}

@@

\title[Controllable Program Regeneration]{\sys: Controllable Program Regeneration\\{\vspace{1em}\normalsize DTU MSc Thesis \\ Advisors: Christian Gram Kahlauge and Nikos Vasilakis}}
\author[Evangelos Lamprou]{Evangelos Lamprou}

@@

\begin{figure}[t]
\centering
  % https://docs.google.com/drawings/d/1JdOfgpaVUy7_EgFyguRXHxFKdmZwyHaiHshnifHG0TQ/edit?usp=sharing
  \includegraphics[width=.9\columnwidth]{figs/kvasir_logic-space.pdf}
  \caption{\textbf{\sys transforms a program over its properties from the abstract logic space to the concrete space.}
  Relationships between properties of the original and regenerated program are inferred 
  from the query in combination with the knowledge base and enforced by \sys plugins.
  }
  \label{fig:logic-to-concrete}
\end{figure}

@@

\begin{table*}[htpb]
\centering
  \caption{\textbf{Benchmark summary}. 
  Benchmark programs come from online repositories, public archives, security research datasets, and often referenced examples in programming culture.
The N column shows the number of programs/functions from each benchmark.
}
  \begin{tabular*}{\textwidth}{llrrll}
\toprule
Benchmark                          & Description                              & N  & LoC & Task                   & Source \\
\midrule
Rosetta Code                       & Simple tasks                             & 16 & 120 & Translation            & \cite{rosettacode} \\
Short utilities                    & npm/PyPi utilities                       & 13 & 1079& Parity                 & \cite{regbench2025} \\
SSCA                               & Sneaky supply-chain attacks              & 3  & 1019& Attack elimination     & \cite{ev:eurosec:2022, ohm2020backstabber,copeland2019frightening} \\
IOCCC                              & Obfuscated C code                        & 2  & 195 & De-obfuscation         & \cite{ioccc} \\
Microbenchmarks                    &                                          & 3  &     &                        & \\
\hspace{.5em} \ttt{flatmap-stream} & Flat-map utility                         &    & 214 & Purity and translation & \cite{es1}  \\
\hspace{.5em} \ttt{Q\_rsqrt}       & Inverse square root function             &    & 16  & Idiomatic rewrite      & \cite{fast_inv_sqrt}  \\
\hspace{.5em} \textsf{rigidDB}     & Fetch artist songs from a music database &    & 33  & Modularization         & \cite{codewithsadeemusicplayer} \\
\midrule
Total                              &                                          & 37 & 2676&                        & \\
\bottomrule
\end{tabular*}
\label{tab:benchmarks}
\end{table*}
